Hierarchical models and seq model fits

### 2025-04-04 documentation/hierarchicalmodels_seqruns.qmd
make fixing values little more robust, clean up
messy working start of k param vector set up

```{r}
fit1a <- fit_model_simplified(runstep = "step1a",
        hierarchical_level     = c("intercept",  "subcluster", "iso"),

@@

@@

>>>>

```{r}
 hierarchical_level     = c("intercept",  "subcluster", "iso")
fit1a <- fit_model_simplified(runstep = "step1a",
        hierarchical_level     =  hierarchical_level,

@@

# summary object

going through what's happening to create the summary object

```{r}
#get_posterior_summaries_simplified(fit1a) 
fit <- fit1a
process_indicator_prefixes = c("")
dm_indicator_prefixes = c("")
process_params = c("mu_raw", "mu_sigma")
dm_params = c("nonse")

```{r}
## part to get the names of parameters to fix
params_to_collect <- dplyr::bind_rows(
  expand.grid(
    prefix = process_indicator_prefixes,
    param = process_params),
  expand.grid(
    prefix = dm_indicator_prefixes,
    param = dm_params)
) |>
  dplyr::mutate(prefixed_param_name = paste0(prefix, param))

# split parameters into those that are "fixable" in local fits and those that
# are "unfixable"
#  unfixable_param_names <- c("local_shrinkage_dm")
# unfixable_param_names <- c("BLA")
fixable_params_to_collect <- params_to_collect |>
  #   dplyr::filter(!param %in% unfixable_param_names) |>
  dplyr::pull(prefixed_param_name)
fixable_params_to_collect 
```

get results for 1 parameter name

get_posterior_summary_one_fixable_param(prefixed_param_name = fixable_params_to_collect[1], fit = fit)
```

when using a fit where things are fixed, fixed values and estimates are combined

(this will be in test case for subnational, we could also add something like 1a and 1b)

```{r}
prefixed_param_name
```

how this summary is used... global fit is used when creaiting the stan data

hier data does not depend on fixed values

Set up hierarchical structures, folow the hierdata.qmd

```{r}
#hierarchical_level <- c("intercept",  "subcluster", "iso")
area <- "iso"
```

Create district index for matching district and district index

```{r}
geo_unit_index <- get_geo_unit_index_data(dat,
                                          hierarchical_levels = c(hierarchical_level), 
                                          area = area)
geo_unit_index
```

```{r}
# use in fit_model:
#hier_data <-  list()
#hier_data[["mu_data"]] <- 
# here we just work with one object:
hier_data <- hierarchical_data(geo_unit_index, hierarchical_level)
#names(hier_data[["mu_data"]])
names(hier_data)
hier_data

```{r}
hier_stan_data <- hierarchical_param_stan_data(
  global_fit = fit1a,
  param_name ="mu",
  param_data = hier_data,
  hierarchical_terms_fixed = hierarchical_level[1:2], 
  hierarchical_sigmas_fixed = hierarchical_level[1:3]
)
names(hier_stan_data)
```

use for non-hierarchical parameters, sigma_y here (vector for the full fpet model)

```{r, eval = FALSE}
 ##### Set up handing of data model hyperparameters ######
  nonse_data <- list(
    "fix_nonse" = as.integer(fix_nonse),
    "nonse_fixed" = numeric(0))
  if (fix_nonse) {
    if (is.null(global_fit)) {
      stop("fix_nonse was set to TRUE, but a global_fit was not provided.")
    }
    for (parname in "nonse"){
      nonse_data[[paste0(parname, "_fixed")]] <- global_fit$post_summ %>% filter(variable == paste0(parname, "[1]")) %>% pull(median)
    }
  }# end fixing dm pars

@@

# trace plots etc
